Motional Quantum Ground-State Cooing of a Single Sodium Atom

### 2017-05-29 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] caption 3 and 4

\begin{figure*}
  \includegraphics[height=5.2cm]{imgs/Na_RSC_schematic.pdf}
  \includegraphics[height=4.5cm]{sequence.pdf}
  \caption{(A) Energy levels and schematics of Raman sideband cooling.
    The Raman transitions has a one photon detuning $\Delta=25GHz$ from the D2 line.
    We use D1 light with $\sigma^-$ polarization to repump atom out of $|F=2,m_F=-1\rangle$
    state to minimize heating on the atom in $|F=2,m_F=-2\rangle$ state.
    (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
    optical tweezer and bias magnetic field.
    (C) Schematics of the cooling sequence. The tweezer is switching at $3\text{MHz}$ to
    reduce light shift during optical pumping. Each cooling cycle consists of $8$ pulses.
    The four axial pulses are addressing two neighboring cooling orders.
    The two pulses in each radial directions are either addressing two neighbering cooling orders
    or having different length on the first order when most of the population are below $n=3$
    towards then end of the cooling sequence.
    \label{f-setup}}
\end{figure*}
\begin{figure}[b]
  \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
  \caption{Matrix elements and heating probabilities as a function of motional state.
    The range plotted covers $99\%$ of the initial thermal distribution.
    (A) Matrix elements for Raman transition in the axial direction showing diviation from
    $\sqrt{n}$ scaling and multiple minimums for different sideband orders.
    (B) Heating probability during the optical pumping step for all three axis.
    Due to the large Lamb-Dicke parameter,
    there is a high probability of heating especially in the axial direction.
    \label{f-ld}}
\end{figure}
\begin{figure*}
  \includegraphics[height=4cm]{imgs/spectrum_r.pdf}
  \includegraphics[height=4cm]{imgs/rabi_flop_r3_0.pdf}
  \includegraphics[height=4cm]{imgs/rabi_flop_r3_p1.pdf}
  \caption{(A) (B) \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[height=4cm]{imgs/spectrum_a1.pdf}
  \includegraphics[height=4cm]{imgs/rabi_flop_a1_0.pdf}
  \includegraphics[height=4cm]{imgs/rabi_flop_a1_p1.pdf}
  \caption{(A) (B) \label{f-axial}}
\end{figure*}

@@

For the more tightly confined radial directions,
we starts the cooling with $\{\bar n_2, \bar n_3\}=????, ????$.
The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
where we can clearly see the first order heating, first order cooling and
second order cooling sidebands.
After applying about 1000 cooling pulses cooling in all three dimensions
starting with cooling on the radial second order,
the Raman spectrum with the same parameter is shown in figure \ref{f-radial}B,
where the first and second order cooling sidebands on both axis are suppressed.
Given the absence of the second order cooling sideband,
we can estimate the ground state probability in each direction based on the height of
the first order cooling and heating sideband to be $????$ and $????$.
Due to the complexity of the sideband structure,
we measured the Rabi flopping on the carrier and heating sideband before and after cooling
(\ref{f-radial}C and \ref{f-radial}D)
as a independent way to obtain the population in different motional states.
Fitting the Rabi flopping data give a ground state probability of $????$ and $????$,
showing good agreement between the two methods.

>>>>

\begin{figure*}
  \includegraphics[height=5.2cm]{imgs/Na_RSC_schematic.pdf}
  \includegraphics[height=4.5cm]{sequence.pdf}
  \caption{(A) Energy levels and schematics of Raman sideband cooling.
    The Raman transitions has a one photon detuning $\Delta=25GHz$ from the D2 line.
    We use D1 light with $\sigma^-$ polarization to repump atom out of $|F=2,m_F=-1\rangle$
    state to minimize heating on the atom in $|F=2,m_F=-2\rangle$ state.
    (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
    optical tweezer and bias magnetic field.
    (C) Schematics of the cooling sequence. The tweezer is switching at $3\text{MHz}$ to
    reduce light shift during optical pumping. Each cooling cycle consists of $8$ pulses.
    The four axial pulses are addressing two neighboring cooling orders.
    The two pulses in each radial directions are either addressing two neighbering cooling orders
    or having different length on the first order when most of the population are below $n=3$
    towards then end of the cooling sequence.
    \label{f-setup}}
\end{figure*}
\begin{figure}[b]
  \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
  \caption{Matrix elements and heating probabilities as a function of motional state.
    The range plotted covers $99\%$ of the initial thermal distribution.
    (A) Matrix elements for Raman transition in the axial direction showing diviation from
    $\sqrt{n}$ scaling and multiple minimums for different sideband orders.
    (B) Heating probability during the optical pumping step for all three axis.
    Due to the large Lamb-Dicke parameter,
    there is a high probability of heating especially in the axial direction.
    \label{f-ld}}
\end{figure}
\begin{figure*}
  \includegraphics[height=4.3cm]{imgs/spectrum_r.pdf}
  \includegraphics[height=4.3cm]{imgs/rabi_flop_r3_0.pdf}
  \includegraphics[height=4.3cm]{imgs/rabi_flop_r3_p1.pdf}
  \caption{Radial Raman sideband spectrum of first order heating, first order cooling and
    second order cooling (A) before and (B) after Raman sideband cooling.
    Rabi flopping on axis 3 (C) carrier and (D) first order heating sideband
    after cooling.
    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $????\%$.
    Horizontal dashed lines in (A) to (D) are total survival and detection efficiency.
    \label{f-radial}}
\end{figure*}

@@

For the more tightly confined radial directions,
we starts the cooling with $\{\bar n_2, \bar n_3\}=????, ????$.
The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
where we can clearly see the first order heating, first order cooling and
second order cooling sidebands.
After applying about 1000 cooling pulses cooling in all three dimensions
starting with cooling on the radial second order,
the Raman spectrum with the same parameter is shown in figure \ref{f-radial}B,
where the first and second order cooling sidebands on both axis are suppressed.
Given the absence of the second order cooling sideband,
we can estimate the ground state probability in each direction based on the height of
the first order cooling and heating sideband to be $????$ and $????$.
Due to the complexity of the sideband structure,
we measured the Rabi flopping on the carrier and heating sideband before and after cooling
(\ref{f-radial}C and \ref{f-radial}D)
as a independent way to obtain the population in different motional states.
Fitting the Rabi flopping data give a ground state probability of $????$ and $????$,
showing good agreement between the two methods.
\begin{figure*}
  \includegraphics[height=4.3cm]{imgs/spectrum_a1.pdf}
  \includegraphics[height=4.3cm]{imgs/rabi_flop_a1_0.pdf}
  \includegraphics[height=4.3cm]{imgs/rabi_flop_a1_p1.pdf}
  \caption{Axial Raman sideban spectrum from first order heating to eighth order cooling
    (A) before and (B) after Raman sideband cooling.
    Rabi flopping on axial (C) carrier and (D) first order heating sideband
    after cooling.
    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $????\%$.
    Horizontal dashed lines in (C) and (D) are total survival and detection efficiency.
    \label{f-axial}}
\end{figure*}
